% -*- TeX -*- -*- Soft -*-

\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{classic}  % style options: 'casual', 'classic', 'banking', 'oldstyle', 'fancy'
\moderncvcolor{blue}     % color options: 'blue', 'orange', 'green', 'red', 'purple', 'grey', 'black'

% Character encoding
\usepackage[utf8]{inputenc}

% Adjust page margins
\usepackage[scale=0.85]{geometry}

% Personal data
\firstname{Kerry}
\familyname{Back}
\title{Curriculum Vitae}
\address{Jones Graduate School of Business}{Rice University}{P.O. Box 2932, Houston, TX 77252--2932}
\email{kerry.e.back@rice.edu}

\usepackage{datetime}
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

\begin{document}

\makecvtitle

\vspace*{-1.5em}
\section{Education}
\cventry{1983}{Ph.D., Economics}{University of Kentucky}{}{}{}
\cventry{1978}{B.A., Economics}{Western Kentucky University}{}{}{}

\section{Employment}

\subsection{Rice University}
\cventry{2023--present}{Finance Area Coordinator}{}{}{}{}
\cventry{2014--present}{J. Howard Creekmore Professor of Finance and Professor of Economics}{}{}{}{}
\cventry{2009--2014}{J. Howard Creekmore Professor of Finance}{}{}{}{}

\subsection{Texas A\&M University}
\cventry{2004--2009}{Jerry and Kay Cox Chair in Business and Thomas W. and Marion K. Leland Memorial Chair in Finance}{}{}{}{}

\subsection{Washington University in Saint Louis}
\cventry{1996--2001, 2002--2003}{Senior Associate Dean, Academic Affairs}{}{}{}{}
\cventry{1996--2004}{Vernon W. and Marion K. Piper Professor of Financial Economics}{}{}{}{}
\cventry{1989--1996}{Visiting Associate, Associate, and Professor of Finance}{}{}{}{}

\subsection{Indiana University}
\cventry{1987--1990}{Associate Professor of Finance}{}{}{}{}

\subsection{University of Pennsylvania}
\cventry{1988--1989}{Visiting Assistant Professor of Economics}{}{}{}{}

\subsection{Northwestern University}
\cventry{1982--1987}{Assistant Professor of Economics}{}{}{}{}

\section{Books}
\begin{enumerate}
\item Back, K., Liu, Hong, and Mark Loewenstein, in preparation, \textit{Pricing and Hedging Derivative Securities: Theory and Methods}, \href{https://book.derivative-securities.org}{book.derivative-securities.org}.
\item Back, K., 2016, \textit{Asset Pricing and Portfolio Choice Theory}, Oxford University Press, New York, 2nd ed.
\item Back, K., 2005, \textit{A Course in Derivative Securities: Introduction to Theory and Computation}, Springer, Berlin. Chinese translation by Shanghai People's Publishing House.
\end{enumerate}

\section{Refereed Articles}
\begin{enumerate}
\item Back, K., Carlin, B., Kazempour, S. M., and C. Xie, forthcoming, ``Discretionary Announcement Timing and Stock Returns,'' \textit{Journal of Finance}.
\item Back, K., Crotty, K., and S. M. Kazempour, 2022, ``Validity, Tightness, and Forecasting Power of Risk Premium Bounds,'' \textit{Journal of Financial Economics}, \textbf{144}, 732--760.
\item Back, K., and P. Barton, 2022, ``Mediation and Strategic Delay in Bargaining and Markets,'' \textit{Journal of Economic Dynamics and Control}, \textbf{141}.
\item Back, K., Liu, R., and A. Teguia, 2020, ``Signaling in OTC Markets: Benefits and Costs of Transparency,'' \textit{Journal of Financial and Quantitative Analysis}, \textbf{55}, 47--75.
\item Back, K., Liu, R., and A. Teguia, 2019, ``Increasing Risk Aversion and Life-Cycle Investing,'' \textit{Mathematics and Financial Economics}, \textbf{13}, 287--302.
\item Back, K., Collin-Dufresne, P., Fos, V., Li, T., and A. Ljungqvist, 2018, ``Activism, Strategic Trading, and Liquidity,'' \textit{Econometrica} \textbf{86}, 1431--1463.
\item Back, K., Crane, A., and K. Crotty, 2018, ``Skewness Consequences of Seeking Alpha,'' \textit{Review of Financial Studies}, \textbf{31}, 4720--4761.
\item Back, K., Crotty, K., and T. Li, 2018, ``Identifying Information Asymmetry in Securities Markets,'' \textit{Review of Financial Studies} \textbf{31}, 2277--2325.
\item Back, K., and K. Crotty, 2015, ``The Informational Role of Stock and Bond Volume,'' \textit{Review of Financial Studies} \textbf{28}, 1381--1427.
\item Back, K., 2014, ``A Characterization of the Coskewness-Cokurtosis Pricing Model,'' \textit{Economics Letters} \textbf{125}, 219--222.
\item Back, K., and S. Baruch, 2013, ``Strategic Liquidity Provision in Limit Order Markets,'' \textit{Econometrica} \textbf{81}, 363--392.
\item Back, K., and D. Paulsen, 2009, ``Open Loop Equilibria and Perfect Competition in Option Exercise Games,'' \textit{Review of Financial Studies} \textbf{22}, 4531--4552.
\item Back, K., and S. Baruch, 2007, ``Working Orders in Limit Order Markets and Floor Exchanges,'' \textit{Journal of Finance} \textbf{61}, 1589--1621.
\item Back, K., and S. Baruch, 2004, ``Information in Securities Markets: Kyle Meets Glosten and Milgrom,'' \textit{Econometrica} \textbf{72}, 433--465.
\item Back, K., and J. Zender, 2001, ``Auctions of Divisible Goods with Endogenous Supply,'' \textit{Economics Letters} \textbf{73}, 29--34.
\item Back, K., Cao, H., and G. Willard, 2000, ``Imperfect Competition among Informed Traders,'' \textit{Journal of Finance} \textbf{55}, 2117--2155 (nominated for Smith-Breeden award).
\item Dybvig, P. H., Rogers, L. C. G., and K. Back, 1999, ``Portfolio Turnpikes,'' \textit{Review of Financial Studies} \textbf{12}, 165--195.
\item Back, K., and H. Pedersen, 1998, ``Long-Lived Information and Intraday Patterns,'' \textit{Journal of Financial Markets} \textbf{1}, 385--402.
\item Back, K., and J. F. Zender, 1993, ``Auctions of Divisible Goods: On the Rationale for the Treasury Experiment,'' \textit{Review of Financial Studies} \textbf{6}, 733--764 (reprinted in Klemperer, Paul, ed., \textit{The Economic Theory of Auctions}, 2000, Edward Elgar).
\item Back, K., 1993, ``Asymmetric Information and Options,'' \textit{Review of Financial Studies} \textbf{6}, 435--472 (received 1993 best paper award from RFS).
\item Back, K., and D. P. Brown, 1993, ``Implied Probabilities in GMM Estimators,'' \textit{Econometrica} \textbf{61}, 971--975.
\item Back, K., 1993, ``Incomplete Markets and Individual Risks,'' \textit{Economic Theory} \textbf{3}, 35--42.
\item Back, K., and D. P. Brown, 1992, ``GMM, Maximum Likelihood, and Nonparametric Efficiency,'' \textit{Economics Letters} \textbf{39}, 23--28.
\item Back, K., 1992, ``Insider Trading in Continuous Time,'' \textit{Review of Financial Studies} \textbf{5}, 387--409.
\item Back, K., 1991, ``Asset Pricing for General Processes,'' \textit{Journal of Mathematical Economics} \textbf{20}, 371--395.
\item Back, K., and S. R. Pliska, 1991, ``On the Fundamental Theorem of Asset Pricing with an Infinite State Space,'' \textit{Journal of Mathematical Economics} \textbf{20}, 1--18.
\item Back, K., 1988, ``Structure of Consumption Sets and Existence of Equilibria in Infinite Dimensional Spaces,'' \textit{Journal of Mathematical Economics} \textbf{17}, 39--49.
\item Back, K., 1988, ``Convergence of Lagrange Multipliers and Dual Variables for Convex Optimization Problems,'' \textit{Mathematics of Operations Research} \textbf{13}, 74--79.
\item Back, K., and S. R. Pliska, 1987, ``The Shadow Price of Information in Continuous Time Decision Problems,'' \textit{Stochastics} \textbf{22}, 151--186.
\item Back, K., 1987, ``A Compact Space of Transitive Locally Non-Satiated Preference Relations,'' \textit{Economics Letters} \textbf{24}, 1987, 253--256.
\item Back, K., 1986, ``Concepts of Similarity for Utility Functions,'' \textit{Journal of Mathematical Economics} \textbf{15}, 129--142.
\item Back, K., 1986, ``Continuity of the Fenchel Transform of Convex Functions,'' \textit{Proceedings of the American Mathematical Society} \textbf{97}, 661--667.
\end{enumerate}

\section{Working Papers}
\begin{enumerate}
\item Back, K., and A. Ober, 2025, ``Performance of Factor Models in a Simple Economy.''
\item Back, K., \c{C}elebi, O., Kakhbod, A., and A. M. Reppen, 2025, ``Segmented Trading Markets.''
\item Back, K., Cocquemas, F., Ekren, I., and A. Lioui, 2024, ``Optimal Transport and Informed Trading in Securities Markets.''
\end{enumerate}

\section{Other Publications}
\begin{enumerate}
\item Back, K., 2010, ``Martingale Pricing,'' \textit{Annual Review of Financial Economics} \textbf{2}, 235--250.
\item Back, K., and S. Baruch, 2010, ``The Kyle Model,'' in R. Cont, ed., \textit{Encyclopedia of Quantitative Finance}, Wiley.
\item Back, K., 2004, ``Incomplete and Asymmetric Information in Asset Pricing Theory,'' in M. Frittelli and W. Runggaldier, eds., \textit{Stochastic Methods in Finance}, Lecture Notes in Mathematics, Springer.
\item Back, K., 1996, ``Yield Curve Models: A Mathematical Review,'' in I. Nelkin, ed., \textit{Option Embedded Bonds: Price Analysis, Credit Risk and Investment Strategies}, Irwin, 3--36.
\item Back, K., 1995, ``Continuous Trading with Asymmetric Information and Imperfect Competition,'' in M. Davis, D. Duffie, W. Fleming, and S. Shreve, eds., \textit{Mathematical Finance}, IMA Volumes in Mathematics and its Applications, Springer-Verlag.
\item Back, K., 1994, ``Review of \textit{Dynamic Asset Pricing Theory} by Darrell Duffie,'' in \textit{Journal of Economic Literature} \textbf{32}, 708--9.
\item Back, K., 1991, ``Review of \textit{Prices in Financial Markets} by Michael U. Dothan,'' in \textit{Review of Financial Studies} \textbf{4}, 221--226.
\end{enumerate}

\section{Editorial Positions}
\cvitem{2022--present}{Associate Editor, Journal of Finance (4th term)}
\cvitem{2001--2011}{Co-Editor, Finance and Stochastics}
\cvitem{1994--1997}{Editor, Review of Financial Studies}
\cvitem{2003--2012}{Associate Editor, Journal of Finance}
\cvitem{1992--1994}{Associate Editor, Review of Financial Studies}
\cvitem{1993--1996}{Associate Editor, Journal of Economic Theory}
\cvitem{1995--1996}{Associate Editor, Journal of Economic Dynamics and Control}
\cvitem{1990--1996}{Associate Editor, Mathematical Finance}
\cvitem{2015--2020}{Associate Editor, Review of Asset Pricing Studies}
\cvitem{2006--2021}{Associate Editor, Mathematics and Financial Economics}
\cvitem{2012--2019}{Advisory Board, Finance and Stochastics}
\cvitem{2012--2015}{Advisory Board, FMA Survey and Synthesis Series}

\section{Ph.D. Committees Chaired and Initial Placements}

\subsection{Rice University}
\cvitem{}{Patrick Blonien (Carnegie Mellon)}
\cvitem{}{Seyed Mohammad Kazempour (LSU)}
\cvitem{}{Paul Barton (SEC)}
\cvitem{}{Alberto Teguia (University of British Columbia)}
\cvitem{}{Ron Liu (University of Nebraska)}
\cvitem{}{Morad Zekhnini (Tulane)}

\subsection{Texas A\&M University}
\cvitem{}{Philipp Illeditsch (Wharton School, University of Pennsylvania)}

\subsection{Washington University in St. Louis}
\cvitem{}{Chris Yung (University of Colorado)}
\cvitem{}{Tao Li (Chinese University of Hong Kong)}
\cvitem{}{Shmuel Baruch (London Business School)}
\cvitem{}{Hal Pedersen (Georgia State)}

\section{Teaching Awards}
\cvitem{2023}{\href{https://www.fma.org/iita2023}{Financial Management Association Innovation in Teaching Award} (joint with Kevin Crotty)}
\cvitem{2001}{Executive Masters in Manufacturing Management Reid Teaching Award, Olin School of Business}
\cvitem{1999}{Executive M.B.A. Reid Teaching Award, Olin School of Business}
\cvitem{1998}{Professional M.B.A. Reid Teaching Award, Olin School of Business}
\cvitem{1997}{Executive M.B.A. Reid Teaching Award, Olin School of Business}

\section{Other Teaching Contributions}
\cvitem{2009--present}{JGSB Finance Ph.D. Coordinator}
\cvitem{}{Creator (with Kevin Crotty) of \href{http://learn-investments.rice-business.org}{Learn Investments @ Rice Business}}
\cvitem{2021--2023}{Advisor to Rice MBA teams that won the \href{https://www.cqa.org/investment_challenge}{Chicago Quantitative Alliance Investment Challenge} in 2021--22 and 2022--23}

\section{Other Awards and Honors}
\cvitem{2024}{Western Finance Association Keynote Speaker}
\cvitem{2018--present}{Member of the Foundation for the Advancement of Research in Financial Economics}
\cvitem{2017--present}{Fellow of the Finance Theory Group}
\cvitem{2016}{Nominated for AFA Board of Directors}
\cvitem{2014}{Charles River Associates prize for best paper in corporate finance, WFA: ``Liquidity and Governance'' (with Tao Li and Alexander Ljungqvist)}
\cvitem{2013}{University of Kentucky Gatton School of Business Alumni Hall of Fame}
\cvitem{2013, 2019}{Jones Graduate School of Business Scholarship Excellence Award}
\cvitem{2007}{Mays Business School Outstanding Research Award}
\cvitem{2000}{Kentucky Economic Association Distinguished Economist}
\cvitem{1999}{Washington University Distinguished Faculty Member}
\cvitem{1993}{Best paper in \textit{Review of Financial Studies}: ``Asymmetric Information and Options''}
\cvitem{1991--1992}{Batterymarch Fellow}

\section{Other Professional Activities}
\cvitem{2015}{Distinguished Visiting Scholar, Securities and Exchange Commission}
\cvitem{2013--2014}{Jon M. Huntsman Presidential Visiting Professor, Utah State University}
\cvitem{2010--2011}{AFA Editor Search Committee}
\cvitem{1994}{AFA Director Nomination Committee}

\subsection{Program Committee}
\cvitem{2003--present}{Utah Winter Finance Conference}
\cvitem{2007--present}{Financial Intermediation Research Society}
\cvitem{2012--2014}{Society for Financial Studies Cavalcade}
\cvitem{1992, 2012--present}{Financial Management Association}
\cvitem{2015--present}{European Finance Association}
\cvitem{2014--present}{Finance Down Under Conference}
\cvitem{1999, 2002}{American Finance Association}
\cvitem{1995--1998, 2002}{Western Finance Association}

\section{Software}
\cvitem{2010}{\textit{SimX}, written with Shmuel Baruch. This package consists of a server (the exchange) and client (for traders). The server is an Erlang program that runs in the Erlang shell and operates an open limit order book for a single stock. Students connect via the client from their computers and use the client to submit and cancel limit orders. Simulations can be run with numerous options concerning the frequency, size and distribution of automated noise and news trades. Students participate in the simulations as dealers or as traders with assigned trades to execute. Performance is measured for dealers in terms of risk-adjusted gains and for traders relative to the volume weighted average price.}

\section{Ad Hoc Reviewer}

\subsection{Finance}
\cvitem{}{Annals of Finance, Journal of Business, European Finance Review, Journal of Finance, Finance and Stochastics, Journal of Financial and Quantitative Analysis, Journal of Financial Economics, Journal of Financial Intermediation, Review of Financial Studies, Mathematical Finance, Review of Quantitative Finance and Accounting, International Journal of Theoretical and Applied Finance}

\subsection{Economics}
\cvitem{}{American Economic Review, Econometrica, Journal of Economic Dynamics and Control, International Economic Review, Review of Economic Studies, Economic Theory, Journal of Economic Theory, Journal of Mathematical Economics, Journal of Money, Credit and Banking, National Science Foundation (Division of Economics), Journal of Political Economy, Economic Inquiry, European Economic Review}

\subsection{Applied Mathematics}
\cvitem{}{Annals of Applied Probability, Applied Mathematics \& Optimization, Israel Science Foundation, Management Science, Mathematical Programming, Mathematics of Operations Research, National Science Foundation (Division of Mathematics), Optimal Control Applications \& Methods, Journal of Optimization Theory and Applications, SIAM Journal on Control and Optimization, Stochastic Processes and their Applications}

\vspace*{1em}
\hfill \textit{Updated: \monthyeardate\today}

\end{document}
